Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript1.2_Ludo.tex

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{connectivity.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Connectivity scheme} 
   \end{figure}

@@

Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization. In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{}.

@@

Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard application. An example of a standard implementation of the Murmex state machines for a scanning system is shown in Fig. BLABLA. Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet. A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely. This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.

@@

A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig. BLABLA, respectively. One personal computer (Dell XXXXX) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Dell YYYYY) to handle and manage the enormous streams of data produced (see next section). Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI XXXX, National Instruments, Austin, USA).

@@

The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Since the clearing procedure with CLARITY produces a linear expansion of about $1.2\times$ \cite{Costantini}, the volume of a clarified mouse brain can be estimated as $\simeq 0.9$ $\text{cm}^3$, while that of a parallelepiped encompassing the sample is expanded to $\simeq 1.6$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$. This means that a cleared mouse brain will be represented with about 7.4 TeraVoxels, while a parallelepiped encompassing the brain will result in 13.3 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 14.8 TB for the whole brain "alone" and 26.6 TB for the parallelepiped (see Table XXXX). However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching. This redundancy expands the size of raw data to 18.3 TB and 32.8 TB, respectively.

@@

With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h. The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h. Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB. Taking into accont the 10\% linear superposition between adjacent stacks, the maximum size of a sample that can be imaged in a single session is about 1.2 $\text{cm}^3$, which is larger than a cleared mouse brain, but smaller than the estimate size of a parallelepiped volume encompassing the entire volume. Therefore imaging should be limited to the portion of the volume where the brain is with rational selection of stacks. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{DataFlow.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:DataFlow} Scheme of the data flow. (A) Data streaming on the microscope. The data is written through the CameraLink connection onto the SSD. From there the data can be transferred via a 10Gb connection to the NAS or to the supercomputing centre CINECA in Bologna. SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage. (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.} 
   \end{figure}

@@

>>>>

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{connectivity.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:connectivity} Schematic views of the hardware (A) and software (B) architectures of the microscope, showing physical and logical connections, respectively. The software architecture scheme clarifies the hierachic structure of the Murmex components. AO analog output, DO digital output, DI digital input.} 
   \end{figure}

@@

Our microscope management software has been written in LabVIEW (National Instruments, Austin, US), as this language is particularly well suited for hardware control and data acquisition through pre-developed methods. An object-oriented programming framework \cite{castagna1997object} has been used, dividing the entire project into well-defined self-contained modules. This framework, besides helping defining the proper scope of each software component, guarantees robustness, ease of maintenance, scalability and reusability. Code is stored on GitHub (www.github.org) to help multiple users developing software simultaneously. The graphical user interface (GUI) provides intuitive control of the apparatus as well as deep personalization. In general, the intrument parameters are already set to optimal values stored on disk, and on-line tips on how to set or change the various settings are provided. Both GUIs and code are developed according to the LabVIEW Style Guide \cite{LabviewStyle}.

@@

Murmex design pattern has twelve pre-defined common states (Initialise, Configure, Start, Stop, Proceed, Update, Reset, Inspect, Inform, Acknowledge, Fetch, Terminate) and a generic state for implementing custom states. Usually, just a few of this states are actually used in standard application. An example of a standard implementation of the Murmex state machine for a scanning system is shown in Fig. BLABLA. Each Murmex component streams information about its current status to its 'observers', other components specified in its configuration file. Using this oberserver/observee hierarchy, it is possible to design large and complex network of different components, running on whatsoever number of computers connected through a local connection or the Internet. A special component, named ServiceManager (also based on Murmex), which must be running on each computer, can start executables remotely. This allows the user to start up a sophisticated configuration with multiple components executed on different computers, but steered from one computer.

@@

A schematic overview of the hardware and software architecture of our light sheet microscope is shown in Fig. BLABLA, respectively. One personal computer (Precision T5600, Dell, Round Rock, USA) controls all the remote hardware components with the exception of the camera, which is controlled by a second, dedicated computer (Precision T7500, Dell, Round Rock, USA) to handle and manage the enormous streams of data produced (see next section). Various instrumentations are addressed either through computer ports (as USB, RS232 and CameraLink) or via analog and/or digital signals generated by a DAQ board (NI PCIe-6353, National Instruments, Austin, USA).

@@

The volume of a mouse brain have been estimated from MRI measurements \cite{Kovacevic2005} as $\simeq 0.5$ $\text{cm}^3$; the same Authors find out that a parallelepiped encompassing the whole brain would have a volume of $\simeq 0.9$ $\text{cm}^3$. Given the pixel size of the camera and the magnification of the system, and assuming a $z$ step of 2 $\mu$m, the voxel size results $0.234\times0.234\times2$ $\mu\text{m}^3$. This means that a mouse brain will be represented with about 4.6 TeraVoxels, while a parallelepiped encompassing the brain will result in 8.2 TeraVoxels. Since the camera produces 16 bit images with no compression, each raw voxel occupies 2 bytes of disk space, resulting in 8.3 TB for the whole brain "alone" and 14.8 TB for the parallelepiped (see Table XXXX). However, image stacks are acquired with a 10\% of linear superposition, which is used later for image stitching. This redundancy expands the size of raw data to 10.2 TB and 18.3 TB, respectively.

@@

With a standard image size of $2048\times 2048$ pixels, and $R_{frame}=44$ Hz, data are produced at a rate $R_{data}=352$ MB/s $\approx 1.2$ TB/h, which results in a volumetric rate $R_{volume} \approx 2\times 10^7$ $\mu\text{m}^3/s$ $\approx 0.07$ $\text{cm}^3$/h. The conversion module can empty the SSD wih an average rate of about 0.7 TB/h, meaning that the SSD is actually filled up during imaging at a rate of about 0.5 TB/h. Imaging sessions should thus be shorter than 21.8 hours: this limits the maximum amount of raw data being acquired continuously to approximately 25.4 TB. This is well above the disk space needed to image the parallelepieped volume encompassing a whole mouse brain. Larger specimens, as rat brain or portion of human brain, must be imaged in consecutive session until faster strategies for image conversion are devised.

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{DataFlow.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:DataFlow} Scheme of the data flow. (A) Data streaming on the microscope. SSD: solid-state disk, RAID: redundant array of independent disks, NAS: network-attached storage. (B) Data production rate versus data conversion rate showing the maximum acquisition time and tomography size feasible before the SSD are filled up.} 
   \end{figure}

@@

\bibitem{LabviewStyle} P. A. Blume, \emph{"The LabVIEW Style Book (National Instruments Virtual Instrumentation Series),"} Prentice Hall PTR (2007).

### 2015-03-25 Neurophotonics/latex-style-files-spie-manuscript/manuscript_Leo.tex

The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 1.4mm$, resulting in $b \simeq 95 \micro m$ and $\text{FWHM}_{\text{axial}} \simeq 2.68 \micro m$. An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner. The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip. From the same data the average FWHM of the Gaussian excitation line over the FOV was calculated. The average FWHM of $0.7\micro m$ was hence set as 1 confocal unit and corresponded to a slit width of 3 horizontal lines on the camera.

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively. The experimentally determined lateral FWHM is larger than the theoretically expected value by a factor of three and this increase is most likely due to The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig. \ref{fig:origin},C).

@@

	\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[height=16cm]{LSMdata.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective). (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm. (C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = 100 µm.} 
   \end{figure}

	Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.

\section{Conclusion}
summary
Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a combination of unprecedented spatio-temporal scale. The impact of this unique measurement technique will continue to revolutionise the field of whole brain connectomics due to its ability to record millions of images over the course of days or even weeks. The data produced in this fashion easily amounts several TB per data set and needs to be stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods. The latter need to be robust, standarised and fully automated processes yet allow for flexible, exploratory and tailored analysis.

@@

\subsubsection{Sample preparation for optical characterisation}
The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS). The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip. The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}. The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space. For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg. Fig. \ref{fig:origin},A) throughout the depth of the image stack. After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths. The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.

>>>>

The need to have an almost uniform resolution in the camera FOV imposes a lower bound to $b$ and thus (according to the previous equations) a limit to the axial resolution. In our setup we adjusted the telescopes in the excitation path in order to have $w \simeq 0.73 mm$, resulting in $b \simeq 346 \micro m$ (corresponding to 72\% of the FOV) and $\text{FWHM}_{\text{axial}} \simeq 5.13 \micro m$. An overview of the relevant formulas concerning the optical properties of a light sheet microscope is given in Table \ref{tab:resolution}. The reader is referred to this table as a quick guide to tailor their microscope to their specific needs.

@@

For optimal imaging it is crucial that the sample-emitted line of fluorescence is in the centre of the rolling shutter at the start of each image acquisition and furthermore travels with the same speed during stack acquisition. To this end the galvo scanners were calibrated using a fluorescein solution in the sample chamber and an image of the focal line was acquired for a set of mirror angles. By fitting each focal line profile to a Gaussian curve the position of the beam main axis was determined and plotted against the voltage applied to the galvo scanner. A linear fit to this data yielded the precise amplitude and offset for each galvo scanner. The finite width of the confocal slit was hereby taken into account such that maximum beam deflection corresponded to the central pixel line of the confocal slit coinciding with the first and last pixel row on the camera chip. From the same data the average FWHM of the Gaussian excitation line over the FOV of the camera was calculated as $(8.60\pm0.67)\micro m$ (n= 14).

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads ($0.51 \micro m$ diameter, Bangs Laboratories). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, was not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively (n=10). The experimentally determined lateral FWHM was larger than the theoretically expected value of $0.26 \micro m$ by a factor of four and this increase was most likely due to.... The experimentally determined axial FWHM was in good agreement with our measured light-sheet thickness of $8.6\micro m$ and marginally larger than the theoretically expected value.

The SNR increased with increasing slit width up to a maximum at a slit width of $7 \micro m$ (Fig. \ref{fig:origin},C).

@@

	%\begin{figure}
   %\begin{center}
   %\begin{tabular}{c}
   %\includegraphics[height=16cm]{LSMdata.eps}
   %\end{tabular}
   %\end{center}
   %\caption{\label{fig:LSMdata} Whole mouse brain tomography. Imaging of whole transgenic mouse brains treated with CLARITY and cleared with TDE 63\% imaged with LSM (Olympus, 25X objective). (A) 3D rendering of a parvalbumin-dTomato brain. (B) 3D rendering of stacks from PV-dTomato mouse brain, GAD-dTomato mouse brain,  PI stained mouse brain, FITC-albumin labeled mouse brain, scale bar = 400 µm. (C,D,E,F) High resolution insert, of the stack corresponding to red boxes in C. Scale bar = 100 µm.} 
   %\end{figure}
	%
	%Everybody take a look at Fig. \ref{fig:LSMdata} because it is the best we have.

\section{Conclusion}

Light sheet microscopy has already been a game changer for large-scale imaging by yielding data with a combination of unprecedented spatio-temporal scale. The impact of this unique measurement technique will continue to revolutionise the field of whole brain connectomics due to its ability to record millions of images over the course of days or even weeks. The data produced in this fashion easily amounts several TB per data set and needs to be stored, transferred, retrieved, processed and visualised necessitating the concurrent development of novel computational interface and analysis methods. The latter need to be robust, standarised and fully automated processes yet allow for flexible, exploratory and tailored analysis.

@@

\subsubsection{Sample preparation for optical characterisation}
The fluorescent beads (CP01F, Bang Laboratories, $0.51 \micro m$ diameter) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS). The low melting point agarose (A-4018, Sigma-Aldrich) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip. The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}. The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space. For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg. Fig. \ref{fig:origin},A) throughout the depth of the image stack. After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths. The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
